Local-global principle for $\K_2$ of Chevalley groups

### 2015-09-27 paper.tex
Minor
Added notes from meeting

%Theorem counters
\numberwithin{equation}{section}
\newcounter{thmcounter} 
\newcounter{lemmacounter}
\newtheorem{thm}[thmcounter]{Theorem}
\newtheorem{prop}[thmcounter]{Proposition}
\newtheorem{cor}[thmcounter]{Corollary}
\newtheorem{lemma}[lemmacounter]{Lemma}
\theoremstyle{definition}
\newtheorem{rem}[equation]{Remark}
\newtheorem{example}[equation]{Example}
\newtheorem{dfn}[equation]{Definition}
\newtheorem{notation}[equation]{Notation}

@@

\title{Local-global principle for $\K_2$ of Chevalley groups}
\keywords {Chevalley groups, Steinberg groups, $K_2$-functor. {\em Mathematical Subject Classification (2010):} 19C09; 20G35}
\author {Andrei Lavrenov, Sergey Sinchuk}
\email {avlavrenov{\it at}gmail.com, sinchukss {\it at} gmail.com}
\date {\today}

@@

>>>>

@@

\title{Local-global principle for $\K_2$ of Chevalley groups}
\keywords {Chevalley groups, Steinberg groups, $K_2$-functor. {\em Mathematical Subject Classification (2010):} 19C09; 20G35}
\author {Andrei Lavrenov, Sergey Sinchuk}
\email {avlavrenov {\it at} gmail.com, sinchukss {\it at} gmail.com}
\date {\today}

@@

\section {Main results}

\begin{dfn}
 Let $u$,$v$ be elements of $B^n$ such that $v^Tu = 0$ and there exists $w \in B^n$ such that $<w,u> = a^N$.
 In this context we define elements $Z^1(u,v)$ and 
\end{dfn}

for each $(u,v) \in \E_n(R) (e_1, e_2)$ we can find $y$ such that $(u,v,y) = g (e_1, e_2, e_3)$.

$w^tu = a^N$, $z^Tv = a^N$, $x^T y = a^N$ + 6 additional orthogonality relations

Computing $g = [Z^{1, N}(u xba^{2N}), Z^{2, N}(ua^{2N},v)]$ 
$$ g = Z^{2, N}(ya^{2N} + uba^{5N},v) {Z^{2, N}(ya^{2N}, v)}^{-1} = Z^{2, N}(uba^{5N},v) = Z^2(uc, v)$$
$$ g = ... = Z^1(u, vc)$$
